The ChEMBL database as Linked Open Data

### 2013-03-26 article.tex
emphasise that the linked RDF URIs are all linked data compatible to our knowledge

This paper presents an update on the ChEMBL-RDF data set, including details of the latest structures
and ontologies used to map ChEMBL to RDF, along with new use cases, showing 
links to other datasets using their RDF URIs to further support research in the life sciences.

>>>>

This paper presents an update on the ChEMBL-RDF data set, including details of the latest structures
and ontologies used to map ChEMBL to RDF, along with new use cases, showing 
links to other datasets using their RDF linked data URIs to further support research in the life sciences.
